Reproducing Palmius’ filtering & imputation

### 2018-03-06 implementingBipolar/implementationReport.Rmd
all

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

I have implemented the filtering algorithm which is descriped in Palmius et al.'s paper. Nick was kind enough to provide pseudocode in addition to his matlab code. His pseudocode is below:
```
data: D(t) recorded data points at tmin ≤ t ≤ tmax. result: D′(t′) filtered data points at t′min ≤ t′ ≤ t′max.
begin
D′ ← D t′←t repeat
t∗ ← t′ where d′ D′ > 100kmh−1 dt
Dsrc ← D′(t∗ − 1)
Ddest ← D′(t∗)
Dˆsrc ← mode(Dsrc)
Dˆdest ← mode(Ddest)
if |Dˆsrc| ≥ |Dˆdest| and |Dˆsrc| > 10 then
Remove all occurrences of Dˆsrc from D′ else if |Dˆdest| ≥ 10 then
Remove all occurrences of Dˆdest from D′ end if
until |Dˆsrc| ≥ 10 and |Dˆdest| < 10 end
◃ Data points with high d′ D. dt
```
Based on that I implemented it and executed it in R. You can see the repository with all my code [here]().

@@

As expected, the high speed between measurement is associated with high accuracy scores (that is, inaccurate measurements). Approximately x percent of measurements in all of 2017 were associated with such jumps.

@@

For my own data in 2017 there was only one location which was excluded (a total of x measurements), which means it is not a very effective filtering algorithm using the original parameters. Moreover, the points which are filtered depend on the length of the data which is taken into account.

@@

@@

## Results following

@@

```{}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(leaflet)
```

@@

I have implemented the filtering algorithm which is descriped in Palmius et al.'s paper. Nick was kind enough to provide pseudocode in addition to his matlab code. His pseudocode is below:
```
data: D(t) recorded data points at tmin ≤ t ≤ tmax. result: D′(t′) filtered data points at t′min ≤ t′ ≤ t′max.
begin
D′ ← D t′←t repeat
t∗ ← t′ where d′ D′ > 100kmh−1 dt
Dsrc ← D′(t∗ − 1)
Ddest ← D′(t∗)
Dˆsrc ← mode(Dsrc)
Dˆdest ← mode(Ddest)
if |Dˆsrc| ≥ |Dˆdest| and |Dˆsrc| > 10 then
Remove all occurrences of Dˆsrc from D′ else if |Dˆdest| ≥ 10 then
Remove all occurrences of Dˆdest from D′ end if
until |Dˆsrc| ≥ 10 and |Dˆdest| < 10 end
◃ Data points with high d′ D. dt
```
Based on that I implemented it and executed it in R. You can see the repository with all my code [here](https://github.com/sobradob/thesis/tree/master/implementingBipolar). Check out the filtering algo and the downsampling algo.

@@

As expected, the high speed between measurement is associated with high accuracy scores (that is, inaccurate measurements). Approximately 1.5% percent of measurements in all of 2017 were associated with such jumps.

@@

For my own data in 2017 there was only one location which was excluded (a total of 0.02% measurements), which means it is not a very effective filtering algorithm using the original parameters. Moreover, the points which are filtered depend on the length of the data which is taken into account.

@@

The difference may be in the quality of the devices recording. I'll check to see the 2015 logs, perhaps it would be more efficient then.

@@

## Results following filtering and downsampling

@@

```{r mapped, echo = F}

raw<- readRDS("raw.rds")
filtered<- readRDS("filtered.rds")

leaflet() %>%
  addTiles() %>%
  addCircles(lng = ~lonF, lat = ~latF, data = raw, color = "#18206F", group = "Raw")%>%
  addCircles(lng = ~lon, lat = ~lat, data=filtered,color = "#DF2935",group = "Filtered")%>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addLayersControl(
    overlayGroups = c("Raw", "Filtered"),
    options = layersControlOptions(collapsed = FALSE)
  )

@@

Palmius uses several imputation algorithms to impute missing data.
